The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-07-27 paper.tex
wrap up first extremely rough draft
still some missing sections :(

@@

\title{The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array}

\author{Michael W. Eastwood}
\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}

\author{Marin M. Anderson}
\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}

\author{Ryan Monroe}
\affiliation{Department of Electrical Engineering, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}

\author{Gregg Hallinan}
\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}

\author{Lincoln Greenhill}
\affiliation{Harvard}

\author{Hugh Garsden}
\affiliation{Harvard}

\author{Stephen Bourke}
\affiliation{Chalmers}

\author{Esayas B. Shume} % contributed ionosphere text
\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}

\begin{abstract}
    I present all-sky maps of the sky from the Owens Valley Long Wavelength Array.
    These maps are created from the application of $m$-mode analysis. \todo{Wednesday}
\end{abstract}

@@

\section{Introduction}

@@

\section{Observations}

\begin{figure}[t]
    \plotone{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

\begin{deluxetable}{cCCCC}
    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
    \tablewidth{0pt}
    \tablehead{
        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} \\
        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)}
    }
    \startdata
        1 & 36.528 & 0.024 & 16.2 \\
        2 & 41.760 & 0.024 & 14.7 \\
        3 & 46.992 & 0.024 & 14.2 \\
        4 & 52.224 & 0.024 & 13.6 \\
        5 & 57.456 & 0.024 & 13.5 \\
        6 & 62.688 & 0.024 & 13.5 \\
        7 & 67.920 & 0.024 & 13.5 \\
        8 & 73.152 & 0.024 & 13.7 \\
    \enddata
\end{deluxetable}

\begin{figure*}[p]
    \gridline{
        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
    }
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}
\begin{figure*}[p]
    \addtocounter{figure}{-1}
    \gridline{
        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
    }
    \caption{(continued)}
\end{figure*}

\section{All-Sky Imaging}

@@

\subsection{$m$-Mode Analysis Image Deconvolution}

@@

\begin{figure}[t]
    \plotone{figures/psf/spw04-psf-45-degrees}
    \caption{
        The computed PSF for the OVRO-LWA for a point source at a declination of $+45^\circ$ and
        frequency of $36.528$ MHz.
    }
    \label{fig:psf}
\end{figure}

@@

\section{Error Analysis}

@@

\begin{figure*}[ht]
    \gridline{
        \fig{figures/smeared-images/before-component-removal-spw14}{0.22\textwidth}{(a)}
        \fig{figures/smeared-images/after-component-removal-spw14}{0.22\textwidth}{(b)}
        \fig{figures/smeared-images/rfi-like-component-spw14}{0.22\textwidth}{(c)}
        \fig{figures/smeared-images/pickup-like-component-spw14}{0.22\textwidth}{(d)}
    }
    \gridline{
        \fig{figures/stripe-maps/spw14-glamour-shot-map-rfi-restored-peeled-rainy-2048-galactic}
            {\textwidth}{(e)}
    }
    \caption{
        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
        smeared along tracks of constant declination. These images are generated using WSCLEAN
        \citep{2014MNRAS.444..606O}, uniform weighting, and baselines shorter than 15 wavelengths
        are flagged. \textbf{(a)} This image shows the initial data before any sources have been
        removed. \textbf{(b)} This image shows the final state after 3 terrestrial sources of
        correlated noise have been removed. \textbf{(c)} This image illustrates the contribution of
        an RFI source towards the north-west that was removed by peeling. \textbf{(d)} This removed
        component is not associated with a dot on the horizon.  Instead it is likely associated with
        common-mode pickup in the analog signal chain. \textbf{(e)} The resulting contamination in
        the full-sky maps from the horizon RFI and common-mode pickup. Note that because these
        contaminating components are not moving sidereally, they tend to generate stripes along
        lines of constant declination. The color scale is in units of Kelvin.
    }
    \label{fig:fitrfi}
\end{figure*}

@@

\section{Results}

@@

\begin{figure*}[p]
    \gridline{
        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \caption{
        Maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA and $m$-mode analysis
        imaging. The properties of each map are summarized in Table~\ref{tab:summary}. The color
        scale is logarithmic and has units of Kelvin. As described in the text, 8 bright sources
        have been subtracted. The small blank region near the bottom of each map corresponds to the
        region of sky within 2 degrees of the Sun at the time of the observations.
    }
    \label{fig:channel-maps}
\end{figure*}

@@

\section{Discussion}

\citet{todo_mishra_2017}

\todo{Wednesday}

>>>>

\newcommand{\astrocaltech}{
    \affiliation{
        Department of Astronomy,
        California Institute of Technology,
        1200 E California Blvd,
        Pasadena, CA 91125
    }
}

@@

\title{
    The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
    with the Owens Valley Long Wavelength Array
}

\author{Michael W. Eastwood}
\astrocaltech

%\author{Marin M. Anderson}
%\affiliation{Department of Astronomy, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}
%
%\author{Ryan Monroe}
%\affiliation{Department of Electrical Engineering, California Institute of Technology, 1200 E California Blvd, Pasadena, CA 91125}

\author{Gregg Hallinan}
\astrocaltech

%\author{Lincoln Greenhill}
%\affiliation{Harvard}
%
%\author{Hugh Garsden}
%\affiliation{Harvard}
%
%\author{Stephen Bourke}
%\affiliation{Chalmers}
%
%\author{Esayas B. Shume} % contributed ionosphere text
%\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}

\begin{abstract}
    I present all-sky maps of the sky from the Owens Valley Long Wavelength Array.
    These maps are created from the application of $m$-mode analysis.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{All-Sky Imaging}

@@

\subsection{CLEAN}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations}

\begin{figure}[ht]
    \plotone{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

\begin{figure}[ht]
    \plotone{figures/psf/spw04-psf-45-degrees}
    \caption{
        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
        declination of $+45^\circ$ and frequency of $36.528$ MHz.
    }
    \label{fig:psf}
\end{figure}

\subsection{The Rainy Day Dataset}

\subsection{Gain Calibration}

\begin{figure*}[p]
    \gridline{
        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
    }
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

%\subsection{Dedistortion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\begin{deluxetable*}{CCCCCC}
    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
    \tablewidth{0pt}
    \tablehead{
        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} &
            \colhead{Noise} & \colhead{Noise} \\
        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)} &
            \colhead{(K)} & \colhead{(Jy)}
    }
    \startdata
    1 & 36.528 & 0.024 & 16.2 & 372.8 \\
    2 & 41.760 & 0.024 & 14.7 & 321.2 \\
    3 & 46.992 & 0.024 & 14.2 & 247.0 \\
    4 & 52.224 & 0.024 & 13.6 & 205.7 \\
    5 & 57.456 & 0.024 & 13.5 & 167.7 \\
    6 & 62.688 & 0.024 & 13.5 & 137.6 \\
    7 & 67.920 & 0.024 & 13.5 & 114.9 \\
    8 & 73.152 & 0.024 & 13.7 &  93.4 \\
    \enddata
\end{deluxetable*}

\begin{figure*}[p]
    \gridline{
        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \caption{
        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
        and $m$-mode analysis imaging. The properties of each map are summarized in
        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
        described in the text, 8 bright sources have been subtracted. The small blank region near
        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
        time of the observations.
    }
    \label{fig:channel-maps}
\end{figure*}

\begin{figure*}[p]
    \gridline{
        \fig{figures/jackknife-maps/4.pdf}
            {0.48\textwidth}{}
        \fig{figures/jackknife-maps/6.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/jackknife-maps/8.pdf}
            {0.48\textwidth}{}
        \fig{figures/jackknife-maps/10.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/jackknife-maps/12.pdf}
            {0.48\textwidth}{}
        \fig{figures/jackknife-maps/14.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/jackknife-maps/16.pdf}
            {0.48\textwidth}{}
        \fig{figures/jackknife-maps/18.pdf}
            {0.48\textwidth}{}
    }
    \caption{
        The jackknife estimated standard deviation corresponding to the maps presented in
        Figure~\ref{fig:channel-maps}. The color scale is logarithmic and has units of Kelvin.
    }
    \label{fig:jackknife-maps}
\end{figure*}

Eight sky maps are presented in Figure~\ref{fig:channel-maps}. Their properties are briefly
summarized in Table~\ref{tab:summary}. In this section we will describe the new imaging technique
used to generate these maps.

%\todo{text}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Error Analysis}

\subsection{Jackknife Resampling}

%\todo{text}

@@

\begin{figure*}[p]
    \gridline{
        \fig{figures/smeared-images/before-component-removal-spw14}{0.22\textwidth}{(a)}
        \fig{figures/smeared-images/after-component-removal-spw14}{0.22\textwidth}{(b)}
        \fig{figures/smeared-images/rfi-like-component-spw14}{0.22\textwidth}{(c)}
        \fig{figures/smeared-images/pickup-like-component-spw14}{0.22\textwidth}{(d)}
    }
    \gridline{
        \fig{figures/stripe-maps/spw14-glamour-shot-map-rfi-restored-peeled-rainy-2048-galactic}
            {\textwidth}{(e)}
    }
    \caption{
        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
        smeared along tracks of constant declination. These images are generated using WSCLEAN
        \citep{2014MNRAS.444..606O}, uniform weighting, and baselines shorter than 15 wavelengths
        are flagged. \textbf{(a)} This image shows the initial data before any sources have been
        removed. \textbf{(b)} This image shows the final state after 3 terrestrial sources of
        correlated noise have been removed. \textbf{(c)} This image illustrates the contribution of
        an RFI source towards the north-west that was removed by peeling. \textbf{(d)} This removed
        component is not associated with a dot on the horizon.  Instead it is likely associated with
        common-mode pickup in the analog signal chain. \textbf{(e)} The resulting contamination in
        the full-sky maps from the horizon RFI and common-mode pickup. Note that because these
        contaminating components are not moving sidereally, they tend to generate stripes along
        lines of constant declination. The color scale is in units of Kelvin.
    }
    \label{fig:fitrfi}
\end{figure*}

@@

@@

@@

%\citet{todo_mishra_2017}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparisons with Other Sky Maps}

%\subsection{The Global Sky Model}
%
%The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z}

\subsection{Haslam 408 MHz Map}

\begin{figure}[t]
    \plotone{figures/haslam/haslam-spectral-index}
    \caption{
        The spectral index between the reprocessed Haslam 408 MHz map and the OVRO-LWA maps
        (degraded to 56 arcmin resolution).  The larger blue patch around the south celestial pole
        corresponds to where the OVRO-LWA map has a blank region.
    }
    \label{fig:haslam-spectral-index}
\end{figure}

The Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H} was reprocessed by
\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources. In
order to compare the OVRO-LWA maps with the lower resolution Haslam map, the OVRO-LWA maps were
degraded to 56 arcmin resolution. A spectral index map computed between the OVRO-LWA maps and the
Haslam map is shown in Figure~\ref{fig:haslam-spectral-index}.

\subsection{Guzm\'{a}n 45 MHz Map}

\begin{figure}[t]
    \plotone{figures/guzman/guzman-comparison}
    \caption{
        This Mollweide projection map compares the fractional difference between the Guzm\'{a}n 45
        MHz map, and the OVRO-LWA map at 46.992 MHz (degraded to $5^\circ$ resolution). A positive
        value indicates regions where the OVRO-LWA map has more emission that the Guzm\'{a}n map,
        and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
        OVRO-LWA map. The red patch around the north celestial pole corresponds to where the
        Guzm\'{a}n map has a blank region.  The larger blue patch around the south celestial pole
        corresponds to where the OVRO-LWA map has a blank region. Note also that the OVRO-LWA map
        has several bright point sources subtracted that are not subtracted from the Guzm\'{a}n map.
    }
    \label{fig:guzman-comparison}
\end{figure}

A direct comparison between the OVRO-LWA at 46.992 MHz and the Guzm\'{a}n 45 MHz map
\citep{2011A&A...525A.138G} can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this
comparison the OVRO-LWA map was degraded to a 5$^\circ$ resolution by convolving with a Gaussian
kernel.  This figure shows that the majority of the galactic synchrotron emission is consistent
between the two maps to better than 5\% however there are patches (particularly near the north
celestial pole) where there is a discrepancy on the order of 20\%.  Off of the galactic plane, the
OVRO-LWA map underestimates the flux compared to the Guzm\'{a}n map by a factor of 20\%. This can be
attributed to the absence of zero-spacing data.

%\subsection{LWA1 Sky Survey}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

%\todo{text}
